Conservator's Corner

### 2018-01-25 pnsac/newsletter/article_MemberInterview.tex
Incorporated changes from Roger and link to Rej's article.

My aviation experience includes 36 years service in the RCAF and nine
years with the Canadian Aeronautics and Space Institute. In the RCAF I
completed radio navigator training, which included communications,
navigation and air gunner. I later qualified as an airborne
interception navigator . My operational experience includes air
transport, search and rescue and training. My assignments included
Navigation Leader, Aircrew Leader, Squadron Commander, Air Command
Navigator and Deputy Commander (COO) of the Air Transport Group. I
logged 9500 hours , mostly on the following aircraft: Beechcraft,
Dakota, North Star , Mitchell, Yukon, Hercules, and Boeing 707. My
staff assignments in Europe included movement control (traffic
management) for 1 Air Division and a tour at The NATO Defense College
in Rome.

@@

My involvement with efforts to conserve North Star 17515 predates
Project North Star. Ottawa area members of the 426 Thunderbird Squadron
Association, mostly retired North Star aircrew, met with the National
Aviation Museum staff to express their concern about the state of the
North Star and proposed volunteer involvement in a preservation effort.
These expressions of concern and interest led to a meeting between the
Association representatives, where General Adamson presented a proposal
for the restoration of the aircraft. It was rejected but assurance was
given that the North Star would be first priority when the new hangar
was completed Also a North Star Trust Fund would be established. Robert
Holmgren, an observer at the meeting, then proceeded to develop a
proposal for volunteers to restore the North Star.
%\begin{figure}[htbp]
%   \vspace{2em}
%   \centering
%   %name of the graphic, without the path AND in EPS format:
%   \includegraphics[scale=0.5]{fwd_cockpit_complete.eps}
%   %caption of the figure 
%   \caption*{\small \em Forward cockpit -- complete.}
%   %label of the figure, which has to correspond to \ref{}:
%   \label{fig:fwd_cockpit_complete}
%\end{figure}

>>>>

My aviation experience includes 36 years service in the RCAF and nine
years with the Canadian Aeronautics and Space Institute. In the RCAF I
completed radio navigator training, which included communications,
navigation and air gunner. I later qualified as an airborne
interception navigator. My operational experience includes air
transport, search and rescue and training. My assignments included
Navigation Leader, Aircrew Leader, Squadron Commander, Air Command
Navigator and Deputy Commander (COO) of the Air Transport Group. I
logged 9500 hours, mostly on the following aircraft: Beechcraft,
Dakota, North Star, Mitchell, Yukon, Hercules, and Boeing 707. My
staff assignments in Europe included movement control (traffic
management) for 1 Air Division and a tour at The NATO Defense College
in Rome.

@@

My involvement with efforts to conserve North Star 17515 predates
Project North Star. Ottawa area members of the 426 Thunderbird Squadron
Association, mostly retired North Star aircrew, met with the National
Aviation Museum staff to express their concern about the state of the
North Star and proposed volunteer involvement in a preservation effort.
These expressions of concern and interest led to a meeting between the
Association representatives, where General Adamson presented a proposal
for the restoration of the aircraft. It was rejected but assurance was
given that the North Star would be first priority when the new hangar
was completed Also a North Star Trust Fund would be established. Robert
Holmgren, an observer at the meeting, then proceeded to develop a
proposal for volunteers to restore the North Star.

%\begin{figure}[htbp]
%   \vspace{2em}
%   \centering
%   %name of the graphic, without the path AND in EPS format:
%   \includegraphics[scale=0.5]{fwd_cockpit_complete.eps}
%   %caption of the figure 
%   \caption*{\small \em Forward cockpit -- complete.}
%   %label of the figure, which has to correspond to \ref{}:
%   \label{fig:fwd_cockpit_complete}
%\end{figure}

### 2018-01-25 pnsac/newsletter/article_PresReport.tex
Incorporated changes from Roger and link to Rej's article.

Our biggest challenge at present is to get our website properly
operational again. A couple of our volunteers with website knowledge
have indicated a willingness to do the necessary work and we are hoping
to have the site working and up to date by the time this issue of the
Nstar Chronicle is published.

>>>>

Our biggest challenge at present is to get our website properly
operational again. A couple of our volunteers with website knowledge
have indicated a willingness to do the necessary work and we are hoping
to have the site working and up to date in the near future.

### 2018-01-25 pnsac/newsletter/article_ProgReport.tex
Incorporated changes from Roger and link to Rej's article.

It was suggested my article for the North Star Chronicle be focused on
the restoration of a certain four engined artifact \#1967.0645. For
details on the work that has been carried out by our dedicated group of
volunteers, I recommend you read my conservation report on the subject.
It is available online: \textcolor{blue}{\texttt{\url{http://www.projectnorthstar.ca}}}
or by email: \textcolor{blue}{\email{rdemers@techno-science.ca}}

>>>>

It was suggested my article for the North Star Chronicle be focused on
the restoration of a certain four engined artifact \#1967.0645. For
details on the work that has been carried out by our dedicated group of
volunteers, I recommend you read my conservation report on the subject.
It is available online: \textcolor{blue}{\texttt{\url{https://documents.techno-science.ca/documents/NorthStarConservationReportOctober2017.pdf}}}
or by email: \textcolor{blue}{\email{rdemers@techno-science.ca}}
